\documentclass[a4paper,12pt]{letter} 
\usepackage{geometry}
\usepackage{hyperref}

\geometry{margin=1in}

\begin{document}

\begin{letter}{ - }

\opening{Dear Hiring Manager,}

I am writing to express my interest in the [Position Title] role at [Company's Name]. As a student pursuing a Bachelor's degree in Computer Science and Engineering at IIIT Kottayam, I have developed a strong foundation in algorithm design, problem-solving, and software development. I am excited about the opportunity to contribute my skills and passion to your team.

During my academic career and internship at Finlatics, I have worked extensively with machine learning models, data analysis, and web development technologies. One notable project was the creation of a sales prediction machine learning model, where I implemented data preprocessing techniques and trained a model to predict future sales trends. Additionally, I have experience analyzing datasets and developing front-end projects, such as cloning the IIIT Kottayam website.

My technical skills include proficiency in multiple programming languages such as C, C++, Python, Java, and MySQL, as well as expertise in web technologies like HTML, CSS, and JavaScript. I am also passionate about machine learning and deep learning, which I have been actively exploring through projects such as wine data classification and Facebook Marketplace data analysis.

What excites me most about [Company's Name] is your commitment to innovative solutions and cutting-edge technologies. I am confident that my background and enthusiasm align with your goals, and I look forward to discussing how I can contribute to your team’s success.

Thank you for considering my application. I am available for an interview at your convenience and can be reached via email at \href{mailto:nissiveronika31@gmail.com}{nissiveronika31@gmail.com} or by phone at 78937 29115.

\closing{Sincerely,}

Nissi Veronika Y\\
IIIT Kottayam\\
\href{https://github.com/nissi31/projects}{GitHub} \quad | \quad \href{https://www.linkedin.com/in/nissi-veronika-2543a0306/}{LinkedIn}

\end{letter}
\end{document}
